\LARGE \bf Eliminating Nonzero Initial States in \\Flexible Systems through Specified Insensitivity Input Shaping

### 2018-04-20 manuscript/manuscript.tex
First stab at MPC for ablation catheter

\input{IC-Shapers.tex}
\input{Design-Params.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Dynamic Model}
\label{sec:intro}
%
\begin{figure}[t!] 
\begin{center}
\includegraphics[width = 2.7in]{Figures/Model} 
\caption{Dynamic model of a two link flexible-arm manipulator} 
\label{fig:model}
\end{center}
\vspace{0.1in}
\end{figure}
%
The dynamic model used in this analysis is shown in Fig.~\ref{fig:model}. A flexible beam is assumed to be fixed at its base, save for rotation allowed about the $\bar{X}$-axis. The rotation of each element is designated by $\theta_{i,j}$, where $i$ is the axis and $j$ is the element number. As depicted in this Figure, each rotation is defined relative to the global coordinate frame. The generalized coordinates are arranged in the following form:
%
\begin{equation}
\label{eq:nodaldisp}
Q_{(3n - 2) \times 1} = 
\begin{bmatrix}
 \theta_{x,1} & 
 \theta_{x,2} &
 \theta_{y,2} & 
 \theta_{z,2} &  
 \dots & 
 \theta_{x,n} & 
 \theta_{y,n} & 
 \theta_{z,n}
\end{bmatrix}^T.
\end{equation}
%
Note the exclusion of the $y$ and $z$ rotations for the first element due to the fixed boundary condition.

@@

The input to the system is given as a torque about the $x_1$-axis applied to the $1_{st}$ element, $\tau_1$, and about the $z_n$-axis applied to the $n^{th}$ element, $\tau_2$. In addition, a known force field, $F$ acts on each element based on its position. This model serves as a first approximation of hydrodynamic forces. Force $F$ has components $f_x$, $f_y$, and $f_z$ defined in the inertial coordinate frame and yields resultant torques on the beam elements. This resultant torque is defined as:
%
\begin{equation}
\label{eq:forced_torque}
\vec{\gamma}_{n} = \int_{0}^{l}\vec{r} \times \vec{F} \mathrm{d}l,
\end{equation}
%
where $\vec{\gamma}_n$ gives the vector of torques applied about each axis within the $n$ cooordinate frame. The integral denotes the summation of each torque on the continuous length of the beam element as a function of its length, $l$. The vector $\vec{r}$ points along the beam within its local coordinate frame. Because each beam element is aligned with this frame, $\vec{r}$ takes the form:
%
\begin{equation}
\label{eq:r_vector}
\vec{r} = l \mathbf{\hat{i}} + 0 \mathbf{\hat{j}} + \mathbf{\hat{k}},
\end{equation}
%
the resolved force can only exert a moment about the $\mathbf{\hat{j}}$ and $\mathbf{\hat{k}}$ axes in this model. The resulting total exogenous input is given by:
%
\begin{equation}
\label{eq:Gamma}
\Gamma_{(3*n - 2) \times 1} = 
\begin{bmatrix}
 0 & 
 0 &
 \gamma_{y,2} & 
 \gamma_{z,2} &  
 \dots & 
 0 & 
 \gamma_{y,n} & 
 \gamma_{z,n}
\end{bmatrix}^T,
\end{equation}
%
where the shape is once again dictated by the nature of the generalized coordinates, (\ref{eq:nodaldisp}).

@@

\bibliographystyle{IEEEtran}
\bibliography{Cardiac_Ablation}

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Dynamic Model}
\label{sec:intro}
%
\begin{figure}[t!] 
\begin{center}
\includegraphics[width = 2.7in]{Figures/Planar_Model} 
\caption{Dynamic model of a two link flexible-arm manipulator} 
\label{fig:model}
\end{center}
\vspace{0.1in}
\end{figure}
%
The dynamic model used in this analysis is shown in Fig.~\ref{fig:model}. A flexible beam is assumed to be fixed at its base. The rotation of each element about the $\bar{Z}$-axis is designated by $\theta_{i}$, where $i$ is the element number. As depicted in this Figure, each rotation is defined relative to the global coordinate frame. The generalized coordinates are arranged in the following form:
%
\begin{equation}
\label{eq:nodaldisp}
Q_{(n \times 1} = 
\begin{bmatrix}
 \theta_{1} & 
 \theta_{2} &
 \dots & 
 \theta_{n} & 
\end{bmatrix}^T.
\end{equation}
%

@@

The input to the system is given as force applied to the distal tip of the $n^{th}$ element, $f$. In addition, a known velocity field, $u$ exerts drag forces on each element. This model serves as a first approximation of hemodynamic forces, where the drag force, $F_D$, exerted on a catheter element is given by:
%
\begin{equation}
\label{eq:drag_force}
F_D = \int_{0}^{l_i} \frac{1}{2}\rho u  C_d D \mathrm{d}l,
\end{equation}
%
where $\rho$ is the mass density of blood, $C_d$ is the drag coefficient of the catheter, $D$ is the diameter of its cross-section, and $l$ is the projected length of the catheter element along the $\bar{X}$-axis. Note that this model ignores wall shear. 
Force $F$ has components $f_x$, $f_y$, and $f_z$ defined in the inertial coordinate frame and yields resultant torques on the beam elements. This resultant torque is defined as:
%
\begin{equation}
\label{eq:forced_torque}
\vec{\gamma}_{n} = \int_{0}^{l}\vec{r} \times \vec{F} \mathrm{d}l,
\end{equation}
%
where $\vec{\gamma}_n$ gives the vector of torques applied about each axis within the $n$ cooordinate frame. The integral denotes the summation of each torque on the continuous length of the beam element as a function of its length, $l$. The vector $\vec{r}$ points along the beam within its local coordinate frame. Because each beam element is aligned with this frame, $\vec{r}$ takes the form:
%
\begin{equation}
\label{eq:r_vector}
\vec{r} = l \mathbf{\hat{i}} + 0 \mathbf{\hat{j}} + \mathbf{\hat{k}},
\end{equation}
%
the resolved force can only exert a moment about the $\mathbf{\hat{j}}$ and $\mathbf{\hat{k}}$ axes in this model. The resulting total exogenous input is given by:
%
\begin{equation}
\label{eq:Gamma}
\Gamma_{(3*n - 2) \times 1} = 
\begin{bmatrix}
 0 & 
 0 &
 \gamma_{y,2} & 
 \gamma_{z,2} &  
 \dots & 
 0 & 
 \gamma_{y,n} & 
 \gamma_{z,n}
\end{bmatrix}^T,
\end{equation}
%
where the shape is once again dictated by the nature of the generalized coordinates, (\ref{eq:nodaldisp}).

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
